### 2019-09-19 manuscript/manuscript.RmD
- small language edits to manuscript - small changes to abstract - small changed to analysis file; e.g., updated order of analyses

  - id            : "1"
    institution   : "University of Hohenheim"
  - id            : ""
    institution   : "Johannes Gutenberg University Mainz"
author_note: |
  All authors contributed extensively to the work presented in this paper. TD, PM, & ST designed the study; PM supervised the data collection; PM administered the data importation; TD & PM wrote the code, ran the models, and analyzed the output data; TD wrote major parts of manuscript, and PM & ST contributed individual sections and comments; ST supervised the project and wrote the grant application (in 2012). 
  The authors declare no competing interests.
  This research was funded by the German Federal Ministry of Education and Research (BMBF) Grant 16KIS0094, awarded to Sabine Trepte.

  This manuscript features online supplementary material that includes the code, additional analyses, and a reproducible version of the manuscript (https://osf.io/4wabh). The data can be downloaded from http://dx.doi.org/10.7802/1937. 
abstract: |
  The privacy paradox states that people's concerns about online privacy are unrelated to their online sharing of personal information. 
  Using a representative sample of the German population, which includes `r knitr::load_cache(label = "load-data", object = "n_complete")` respondents who were interviewed at three waves separated by 6 months, we investigate the privacy paradox from a longitudinal perspective, differentiating between-person relations from within-person effects.
  Results of a cross-lagged panel model with random intercepts revealed that people who were more concerned about their online privacy than others also shared slightly less personal information online and had substantially more negative attitudes toward the online  sharing of personal information than others (between-person level). 
  Next, people who were more concerned than usual also shared slightly less information than usual (within-person level). 
  At the same time, we found no long-term effects of privacy concerns on information sharing or attitudes 6 months later.
  Together, the results provide further evidence against the privacy paradox.
keywords          : "privacy paradox, privacy concerns, information disclosure, longitudinal analysis, structural equation modeling"
wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
bibliography      : 
  - [../bibliography/references.bib]
  - [../bibliography/r-references.bib]
lang              : "english"
class             : "man"
mask              : no
output            : papaja::apa6_pdf
# output            : papaja::apa6_word
header-includes:
  - \setlength{\parskip}{0em}
  - \raggedbottom
editor_options: 
  chunk_output_type: inline
---
```{r knitr-set-up}
knitr::opts_chunk$set(echo=F, error=F, message=F, tidy=T, warning=F)
```

@@

# load r-bib
r_citations <- cite_r("../bibliography/r-references.bib", 
                      footnote = FALSE, 
                      pkgs = c("GGally", "ggplot2", "lavaan", "lme4", "magrittr", 
                               "MissMech", "papaja", "psych", "pwr", "RVAideMemoire", 
                               "semTools", "sjstats", "tidyverse", "td"), 
                      withhold = FALSE)
```

@@

The privacy paradox states that information disclosure practices of Internet users are problematic: 
Although many people are concerned about their online privacy, they still tend to share plenty of personal information on the web [e.g., @acquistiLossesGainsHyperbolic2003]. 
The privacy paradox and its underlying theoretical conundrum is hence of considerable interest to society---it is discussed in newspapers [@freanFindingSolutionsPrivacy2017], Wikipedia [@wikipediaPrivacyConcernsSocial2018], designated websites [@newyorkpublicradioPrivacyParadox2018], books [@treptePrivacyOnlinePerspectives2011], and top-tier academic journals [@acquistiPrivacyHumanBehavior2015].
If the privacy paradox really exists, it should inspire worry: 
It would suggest that online behavior is irrational and that people are revealing too much of their personal lives to unknown third parties, which can foster potentially unintended consequences such as commodification [@sevignaniPrivacyCapitalismAge2016], inappropriate recontextualization [@boydTakenOutContext2008], or increased predictability of future behavior [@bagrowInformationFlowReveals2019].
In conclusion, understanding why people disclose information online and whether this is paradoxical or not represents an important challenge for scholars in the social sciences.

@@

It has been argued that privacy attitudes could 'bridge the gap' between concerns and information sharing [e.g., @dienlinPrivacyParadoxRelic2015]. 
In contrast to privacy concerns, privacy attitudes capture a more explicit, fluctuating cognitive appraisal. 
Although both variables are related to information disclosure, attitudes are likely to be the better predictor. 
This reasoning follows the rational choice paradigm [@simonBehavioralModelRational1955], which maintains that behavior is always, at least in part, influenced by convictions, attitudes, and cost-benefit analyses. 
Likewise, evolutionary psychology also suggests that although emotions guide behavior in the long run, it is more adaptive if behavior instead reflects a cognitive appraisal; 
a tenet arguably reflected best by the phylogenetic development of the neocortex or the general dominion of the human race.
These rationales have also found some empirical support. 
For example, a study of 1,042 youths from Belgium found that the relation between privacy attitudes and disclosure of personal information was strong (_r_ = .56), whereas the relation between privacy concerns and disclosure was moderate [_r_ = -.29; @heirmanPredictingAdolescentsDisclosure2013].

@@

Concerning the potential long-term relations of privacy attitudes, the same situation exists here as mentioned above:
Given that no prior research exists on long-term relations, several scenarios seem plausible.
For example, attitudes could either have long-term relations or not, and information sharing could either foster or diminish privacy attitudes.

@@

We follow the recommendation by @lakensJustifyYourAlpha2017 and first justify the choice of our alpha level. 
We determined adequate error margins by considering the potential implications of both false positive and false negative findings (i.e., alpha and beta errors): 
On the one hand, if we committed an alpha error, we would wrongfully conclude that people's concerns and behaviors are consistent. 
Communicating such a false result to the public would unjustly reassure and placate people when they should instead be more alert.
On the other hand, if we committed a beta error, we would wrongfully conclude that individuals behave paradoxically.
Communicating such a false result would unjustly accuse people of implausible behavior, potentially causing unnecessary distress or reactance.
We consider both errors to be equally detrimental. 
Hence, we chose to use error rates that are balanced.
Next, we set a maximum error rate of 5% for both alpha and beta. 
As the smallest effect size of interest [SESOI; @lakensPerformingHighpoweredStudies2014], we chose to consider effects that are at least small [i.e., standardized coefficients above $\beta$ = `r sesoi %>% my_round("beta")`; @cohenPowerPrimer1992] as able to offer empirical support for our theoretical hypotheses; significantly smaller effects were not considered able to offer support.
The six hypotheses were tested with a one-tailed approach and the six research questions with a two-tailed approach.
On the basis of the balanced alpha-beta approach with a maximum error probability of `r alpha %>% round(3) * 100`%, a desired power of `r power %>% round(3) * 100`%, and an SESOI of $\beta$ = `r sesoi`, we calculated that we needed a minimum sample size of `r dollar_format(prefix = "")(round(n_apriori, 0))` respondents. 
Given the final sample size of `r dollar_format(prefix = "")(n)` respondents (see below), alpha and beta errors were balanced for our hypotheses (research questions) when we used a critical alpha of `r alpha_balanced_h  %>% round(3) * 100`% (`r alpha_balanced_rq  %>% round(3) * 100`%), resulting in a power of `r power_balanced_h %>% round(3) * 100`%  (`r power_balanced_rq %>% round(3) * 100`%) to detect small effects.

The data were analyzed by means of a random-intercept cross-lagged panel model (RI-CLPM) [@hamakerCritiqueCrosslaggedPanel2015], a method that already has been used for similar research questions [@dietvorstAdolescentPerceptionsParental2018].
Note that in contrast to regular cross-lagged panel models (CLPMs), RI-CLPMs allow to separate between-person variance from within-person variance. 
We used factor scores as observed variables to represent the variables' latent structure more closely.
We tested H1, H3.1, and H3.2 by correlating the random intercepts, which represent the respondents' individual mean scores across all three waves.
We tested H2, H4.1, and H4.2 by correlating the respondents' within-person variance at T1, which captures their specific deviation at T1 from their overall score.
We tested all research questions by regressing variables on all other measures obtained 6 months earlier.
Given that we had three points of measurement, this resulted in two estimates for each Research Question.
As we did not expect longitudinal effects to differ across time, they were constrained to be equal across all waves, thereby producing one single general measure of each effect instead of two time-specific ones.
Fit was assessed according to the common criteria as described by @klinePrinciplesPracticeStructural2016. 
The final model fit the data well, `r fit_txt(fit_riclpm)`.

For the analyses, coding, and typesetting, we used `r r_citations`.
The code, additional analyses, and a reproducible version of the manuscript can be accessed in the Online Supplementary Material (OSM) at https://osf.io/4wabh.

@@

This study is part of a large-scale project which investigates the development of privacy and self-disclosure, including several other variables. 
Other publications linked to the project can be accessed at https://osf.io/y35as/.
The data come from a longitudinal, paper-and-pencil questionnaire study, in which a representative sample of the German population (16 years and older) was surveyed on overall five occasions.
The data can be downloaded from http://dx.doi.org/10.7802/1937.

The first three waves were collected from May 2014 to May 2015, with intervals of 6 months each.
The last two waves, collected on May 2016 and May 2017, had an interval of one year.
Because we hypothesized the effects to take place across half a year, the last two waves were not included in the analyses presented here.
First, a sample of 14,714 potential respondents was drawn from a representative omnibus survey in Germany (ADM master sample), employing a random last-two-digit dialing procedure. 
In this CATI screening, 5,286 respondents agreed to participate in all following waves.

Wave 1 was completed by 3,278 respondents (response rate: `r round((1 - (3278 / 5286)) * 100, 0)`%), Wave 2 by 2,448 respondents (attrition rate: `r round((1 - (2448 / 3278)) * 100, 0)`%), and Wave 3 by 2,021 respondents (attrition rate: `r round((1 - (2021 / 2448)) * 100, 0)`%). 
We filtered respondents who never used the Internet at all waves, answered fewer than 50% of the items in each scale for at least one wave, provided inconsistent birth-dates across measurements, or who did not report sociodemographic variables.
The final sample consisted of *n* = `r dollar_format(prefix = "")(n_complete)` respondents.

In the final sample, the rate of missing data was `r na_per %>% round(2)`%. 
Visual inspection of the missing value patterns as well as the non-parametric test by @R-MissMech suggested that all missing values could be considered missing at random (*p* `r test_mar_p %>% my_round("p_txt")`). 
Therefore, Full Information Maximum Likelihood (FIML) estimation was conducted using all available data.

The average age was `r round(age_m, 0)` years (*SD* = `r round(age_sd, 0)` years), and `r (round(male_per, 2) - 1) * 100`% were male. 
About `r round(edu_col_per, 0)`% reported that they had graduated from college.

@@

To measure respondent's level of information disclosure, they were asked to indicate how often they disclosed 10 different pieces of information on the Internet. 
The exact question was: "How often do you disclose the following pieces of information online (i.e., on the Internet)?" 
Each item was answered on a 5-point scale ranging from 1 (*never*) to 5 (*daily*). 
Factor analyses suggested a second-order factor structure with five first-order factors. 
The first first-order factor subsumed financial and medical information, the second covered first and last name, the third included place of residence and street (including house number), the fourth email address and phone number, and the fifth contained information about education and current job. 
The means were _M_~t1~ = `r desc[["t1_inf_sha_beh_m_mean"]] %>% my_round(2)`, 
_M_~t2~ = `r desc[["t2_inf_sha_beh_m_mean"]] %>% my_round(2)`, 
_M_~t3~ = `r desc[["t3_inf_sha_beh_m_mean"]] %>% my_round(2)`, 
and the standard deviations _SD_~t1~ = `r desc[["t1_inf_sha_beh_m_sd"]] %>% my_round(2)`, 
_SD_~t2~ = `r desc[["t2_inf_sha_beh_m_sd"]] %>% my_round(2)`, and
_SD_~t3~ = `r desc[["t3_inf_sha_beh_m_sd"]] %>% my_round(2)`.
The model fit the data adequately,
`r fit_txt(fit_inf_sha_beh_4)`.
The reliability was high ($\omega$~t1~ = `r reliabilityL2(fit_inf_sha_beh_4, "t1_inf_sha_beh_f")[["omegaL2"]] %>% my_round("std")`, $\omega$~t2~ = `r reliabilityL2(fit_inf_sha_beh_4, "t2_inf_sha_beh_f")[["omegaL2"]] %>% my_round("std")`, $\omega$~t3~ = `r reliabilityL2(fit_inf_sha_beh_4, "t3_inf_sha_beh_f")[["omegaL2"]] %>% my_round("std")`).
Overall, `r icc_inf_sha_beh$ICC_adjusted * 100 %>% round(0)`% of the measure's variance was explained by differences between persons.

@@

Hypothesis 1 predicted that people reporting higher concerns about online privacy than others would also be less likely to share personal information online than others.
Results revealed that the random intercepts of the two variables were significantly correlated (`r coeffs_txt(fit_riclpm, "cor_b_2", one_sided = TRUE)`). 
Respondents who---on average across all three waves---were more concerned about their privacy than others also shared slightly less personal information online.
The effect was small.
However, when looking at the standardized effect's confidence interval ($\beta$ = `r effect_std_ci[["est.std"]] %>% my_round("std")`, 95% CI [`r effect_std_ci[["ci.lower"]] %>% my_round("std")`, `r  effect_std_ci[["ci.upper"]] %>% my_round("std")`]), it was not significantly smaller than our SESOI of $beta$ = .10.
Thus, Hypothesis 1 was supported.

Hypothesis 2 proposed that if people perceived more concerns about their online privacy than they usually do, they would also share less personal information online than they usually do.
Results revealed a small significant correlation (`r coeffs_txt(fit_riclpm, "cor_w_2", one_sided = TRUE)`), suggesting that if respondents were more concerned about their online privacy at T1 than usual, they also shared less personal information online at T1.
In conclusion, the results supported Hypothesis 2.

@@

Hypothesis 3.1 predicted that people who perceived more privacy concerns than others would also hold more negative attitudes toward the online sharing of personal information than others. 
The results revealed a medium-sized negative correlation between the two variables on the between-person level (`r coeffs_txt(fit_riclpm, "cor_b_1", one_sided = TRUE)`). 
Thus, people who---on average across all three waves---reported being more concerned about their online privacy relative to the rest of the sample, were also moderately more likely to hold a more negative attitude toward the online sharing of personal information, thereby supporting Hypothesis 3.1.
Hypothesis 3.2 posited that people who held more positive attitudes toward the online sharing of personal information than others would also share more personal information online than others. 
Results showed a very strong between-person correlation between the two variables (`r coeffs_txt(fit_riclpm, "cor_b_3", one_sided = TRUE)`): 
When averaged across all three waves, if people had more positive attitudes toward the online sharing of personal information than others, they were much more likely to actually share personal information online.
In conclusion, the results supported Hypothesis 3.2.

Hypothesis 4.1 proposed that people who perceived more privacy concerns than usual would also hold more negative attitudes toward the online sharing of personal information than usual. 
The results did not reveal a significant effect (`r coeffs_txt(fit_riclpm, "cor_w_1", one_sided = TRUE)`). 
Hypothesis 4.2 proposed that people who held more positive attitudes toward the online sharing of personal information than usual would also share more personal information online than usual. 
Results showed a moderate within-person correlation between the two variables (`r coeffs_txt(fit_riclpm, "cor_w_3", one_sided = TRUE)`), indicating that when respondents had more positive attitudes toward the online sharing of personal information at T1 than usual, they also shared more personal information online.
In conclusion, the results supported Hypothesis 4.2.

With Research Question 2.1, we analyzed the longitudinal relations of concerns about online privacy and positive attitudes toward the online sharing of personal information. 
No significant effect was found, `r coeffs_txt(fit_riclpm, "b1")`.
Regarding Research Question 2.2, again no significant longitudinal relations emerged between privacy attitudes and privacy concerns 6 months later `r coeffs_txt(fit_riclpm, "a2")`.

@@

Table \@ref(tab:Results1) presents an overview of all results and the OSM presents additional information and supplementary analyses (e.g., results of the RI-CLPM without socio-demographic control variables or results of alternative multilevel regression models).

@@

apa_table(
  tab_results
  , caption = "Parameter Estimates Obtained in the Random-Intercept Cross-Lagged Panel Model"
  , note = paste0("The between-person correlations represent interpersonal relations. For example, results showed that people who were more concerned than others, averaged across all 3 waves, also shared less information than others. The within-person parameters reflect how intrapersonal changes in one variable are related to intra-personal changes in another. For example, results showed that if a person was more concerned at T1 than he or she usually is, he or she also shared less information than usual.")
  , font_size = "small"
  , stub_indents = list("Between-person correlations across all waves" = c(1:3),
                        "Within-person correlations at T1" = c(4:6),
                        "Within-person effects across 6 months" = c(7:12))
  , align = c("l", rep("r", 6))
  , escape = FALSE
  , col_spanners = list(`95\\% CI` = c(3, 4))
#  , placement = "h"
)
```

@@

Current research on the privacy paradox revealed that a significant relation between concerns about online privacy and the online sharing of personal information exists and that it is small [e.g., @baruhOnlinePrivacyConcerns2017]. 
However, whereas the theoretical premise of the privacy paradox actually addresses a within-person effect,
empirical studies have analyzed between-person relations.
On the basis of a representative sample of the German population, from which three waves of data separated by 6 months were collected, we have hence analyzed the privacy paradox by differentiating general between-person relations, short-term within-person relations, as well as long-term within-person effects.

>>>>

  - id            : "1"
    institution   : "University of Hohenheim"
  - id            : "2"
    institution   : "Johannes Gutenberg University Mainz"
author_note: |
  All authors contributed extensively to the work presented in this paper. TD, PM, & ST designed the study; PM supervised the data collection; PM administered the data importation; TD & PM wrote the code, ran the models, and analyzed the output data; TD wrote major parts of manuscript, and PM & ST contributed individual sections and comments; ST supervised the project and wrote the grant application (in 2012). 
  The authors declare no competing interests.
  This research was funded by the German Federal Ministry of Education and Research (BMBF) Grant 16KIS0094, awarded to Sabine Trepte.

  This manuscript features online supplementary material that includes the code, additional analyses, and a reproducible version of the manuscript (https://osf.io/4wabh). The data can be downloaded from http://dx.doi.org/10.7802/1937. 
abstract: |
  The privacy paradox states that people's concerns about online privacy are unrelated to their online sharing of personal information. 
  Using a representative sample of the German population, which includes `r knitr::load_cache(label = "load-data", object = "n_complete")` respondents who were interviewed at three waves separated by 6 months, we investigate the privacy paradox from a longitudinal perspective, differentiating between-person relations from within-person effects.
  Results of a cross-lagged panel model with random intercepts revealed that people who were more concerned about their online privacy than others also shared slightly less personal information online and had substantially more negative attitudes toward information sharing (between-person level). 
  Next, people who were more concerned than usual also shared slightly less information than usual (within-person level). 
  At the same time, we found no long-term effects of privacy concerns on information sharing or attitudes 6 months later.
  Together, the results provide further evidence against the privacy paradox.
keywords          : "privacy paradox, privacy concerns, information sharing, longitudinal analysis, structural equation modeling"
wordcount         : "`r wordcountaddin::word_count('manuscript.Rmd')`"
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
bibliography      : 
  - [../bibliography/references.bib]
  - [../bibliography/r-references.bib]
lang              : "english"
class             : "man"
mask              : no
output            : papaja::apa6_pdf
# output            : papaja::apa6_word
header-includes:
  - \setlength{\parskip}{0em}
  - \raggedbottom
editor_options: 
  chunk_output_type: inline
---
```{r knitr-set-up}
knitr::opts_chunk$set(echo=F, error=F, message=F, tidy=T, warning=F)
```

@@

# load r-bib
r_citations <- cite_r("../bibliography/r-references.bib", 
                      footnote = FALSE, 
                      pkgs = c("GGally", "ggplot2", "lavaan", "lme4", "magrittr", 
                               "MissMech", "MVN", "papaja", "psych", "pwr",  
                               "semTools", "sjstats", "tidyverse", "td"), 
                      withhold = FALSE)
```

@@

The privacy paradox states that the information disclosure practices of Internet users are problematic: 
Although many people are concerned about their online privacy, they still tend to share plenty of personal information on the web [e.g., @acquistiLossesGainsHyperbolic2003]. 
The privacy paradox and its underlying theoretical conundrum is hence of considerable interest to society---it is discussed in newspapers [@freanFindingSolutionsPrivacy2017], Wikipedia [@wikipediaPrivacyConcernsSocial2018], designated websites [@newyorkpublicradioPrivacyParadox2018], books [@treptePrivacyOnlinePerspectives2011], and top-tier academic journals [@acquistiPrivacyHumanBehavior2015].
If the privacy paradox really exists, it should inspire worry: 
It would suggest that online behavior is irrational and that people are revealing too much of their personal lives to unknown third parties, which can foster potentially unintended consequences such as commodification [@sevignaniPrivacyCapitalismAge2016], inappropriate recontextualization [@boydTakenOutContext2008], or increased predictability of future behavior [@bagrowInformationFlowReveals2019].
In conclusion, understanding why people disclose information online and whether this is paradoxical or not represents an important challenge for scholars in the social sciences.

@@

It has been argued that privacy attitudes could 'bridge the gap' between concerns and information sharing [e.g., @dienlinPrivacyParadoxRelic2015]. 
In contrast to privacy concerns, privacy attitudes capture a more explicit, fluctuating cognitive appraisal. 
Although both variables are related to information disclosure, attitudes are likely to be the better predictor. 
This reasoning follows the rational choice paradigm [@simonBehavioralModelRational1955], which maintains that behavior is always, at least in part, influenced by convictions, attitudes, and cost-benefit analyses. 
Likewise, evolutionary psychology also suggests that although emotions guide behavior in the long run, it is more adaptive if behavior instead reflects a cognitive appraisal; 
a tenet arguably reflected best by the phylogenetic development of the neocortex or, if you want, the general dominion of the human race.
These rationales have also found some empirical support. 
For example, a study of 1,042 youths from Belgium found that the relation between privacy attitudes and disclosure of personal information was strong (_r_ = .56), whereas the relation between privacy concerns and disclosure was more moderate [_r_ = -.29; @heirmanPredictingAdolescentsDisclosure2013].

@@

Concerning the potential long-term relations of privacy attitudes, we are confronted with the same situation mentioned above:
Given that we are not aware of research on long-term relations, several scenarios seem plausible.
For example, attitudes could either have long-term relations or not, and information sharing could either foster privacy attitudes or diminish them.

@@

We follow the recommendation by @lakensJustifyYourAlpha2018 and first justify the choice of our alpha level. 
We determined adequate error margins by considering the potential implications of both false positive and false negative findings (i.e., alpha and beta errors): 
On the one hand, if we committed an alpha error, we would wrongfully conclude that people's concerns and behaviors are consistent. 
Communicating such a false result to the public might unjustly reassure and placate people when they should instead be more alert.
On the other hand, if we committed a beta error, we would wrongfully conclude that individuals behave paradoxically.
Communicating such a false result would unjustly accuse people of implausible behavior, potentially causing unnecessary distress or reactance.
We consider both errors to be equally detrimental. 
Hence, we chose to use error rates that are balanced.
Next, we set a maximum error rate of 5% for both alpha and beta. 
As the smallest effect size of interest [SESOI; @lakensEquivalenceTestingPsychological2018], we chose to consider effects that are at least small [i.e., standardized coefficients above $\beta$ = `r sesoi %>% my_round("beta")`; @cohenPowerPrimer1992] as able to offer empirical support for our theoretical hypotheses; 
significantly smaller effects were not considered able to offer support.
The six hypotheses were tested with a one-tailed approach and the six research questions with a two-tailed approach.
On the basis of the balanced alpha-beta approach with a maximum error probability of `r alpha %>% round(3) * 100`%, a desired power of `r power %>% round(3) * 100`%, and an SESOI of $\beta$ = `r sesoi`, we calculated that we needed a minimum sample size of `r dollar_format(prefix = "")(round(n_apriori, 0))` respondents. 
Given the final sample size of `r dollar_format(prefix = "")(n)` respondents (see below), alpha and beta errors were balanced for our hypotheses (research questions) when we used a critical alpha of `r alpha_balanced_h  %>% round(3) * 100`% (`r alpha_balanced_rq  %>% round(3) * 100`%), resulting in a power of `r power_balanced_h %>% round(3) * 100`%  (`r power_balanced_rq %>% round(3) * 100`%) to detect small effects.

The data were analyzed by means of a random-intercept cross-lagged panel model (RI-CLPM) [@hamakerCritiqueCrosslaggedPanel2015], a method that already has been used for similar research questions [@dietvorstAdolescentPerceptionsParental2018].
Note that in contrast to regular cross-lagged panel models (CLPMs), RI-CLPMs allow to separate between-person variance from within-person variance. 
We used factor scores as observed variables to represent the variables' latent structure more closely.
We tested H1, H3.1, and H3.2 by correlating the random intercepts, which represent the respondents' individual mean scores across all three waves.
We tested H2, H4.1, and H4.2 by correlating the respondents' within-person variance at T1, which captures their specific deviation at T1 from their overall score.
We tested all research questions by regressing variables on all other measures obtained 6 months earlier.
Given that we had three points of measurement, this resulted in two estimates for each research question.
As we did not expect longitudinal effects to differ across time, they were constrained to be equal across all waves, which produces one single general measure of each effect instead of two time-specific ones.
Fit was assessed according to the common criteria as described by @klinePrinciplesPracticeStructural2016. 
The final model fit the data well, `r fit_txt(fit_riclpm)`.

For the analyses, coding, and typesetting, we used `r r_citations`.
The code, additional analyses, and a reproducible version of this manuscript can be accessed in the Online Supplementary Material (OSM) at https://osf.io/4wabh.

@@

This study is part of a large-scale project which investigates the development of privacy and self-disclosure, including several other variables. 
Other publications linked to the project can be accessed at https://osf.io/y35as/.
The data come from a longitudinal paper-and-pencil questionnaire study, in which a representative sample of the German population (16 years and older) was surveyed on overall five occasions.
The data can be downloaded from http://dx.doi.org/10.7802/1937.

The first three waves were collected from May 2014 to May 2015, with intervals of 6 months each.
The last two waves, collected on May 2016 and May 2017, had an interval of one year.
Because we hypothesized the effects to take place across half a year, the last two waves were not included in the analyses presented here.
First, a sample of 14,714 potential respondents was drawn from a representative omnibus survey in Germany (ADM master sample), employing a random last-two-digit dialing procedure. 
In this CATI screening, 5,286 respondents agreed to participate in all following waves. 
Wave 1 was completed by 3,278 respondents (response rate: `r round((1 - (3278 / 5286)) * 100, 0)`%), Wave 2 by 2,448 respondents (attrition rate: `r round((1 - (2448 / 3278)) * 100, 0)`%), and Wave 3 by 2,021 respondents (attrition rate: `r round((1 - (2021 / 2448)) * 100, 0)`%). 
We filtered respondents who never used the Internet at all waves, answered fewer than 50% of the items in each scale for at least one wave, provided inconsistent birth-dates across measurements, or who did not report sociodemographic variables.
The final sample consisted of *n* = `r dollar_format(prefix = "")(n_complete)` respondents.

In the final sample, the rate of missing data was `r na_per %>% round(2)`%. 
Visual inspection of the missing value patterns as well as the non-parametric test by @R-MissMech suggested that all missing values could be considered missing at random (*p* `r test_mar_p %>% my_round("p_txt")`). 
Therefore, Full Information Maximum Likelihood (FIML) estimation was conducted using all available data.
The average age was `r round(age_m, 0)` years (*SD* = `r round(age_sd, 0)` years), and `r (round(male_per, 2) - 1) * 100`% were male. 
About `r round(edu_col_per, 0)`% reported that they had graduated from college.

@@

To measure respondent's level of information disclosure, they were asked to indicate how often they disclosed 10 different pieces of information on the Internet. 
The exact question was: "How often do you disclose the following pieces of information online (i.e., on the Internet)?" 
Each item was answered on a 5-point scale ranging from 1 (*never*) to 5 (*daily*). 
Factor analyses suggested a second-order factor structure with five first-order factors. 
The first first-order factor subsumed financial and medical information, the second first and last name, the third place of residence and street (including house number), the fourth email address and phone number, and the fifth information about education and current job. 
The means were _M_~t1~ = `r desc[["t1_inf_sha_beh_m_mean"]] %>% my_round(2)`, 
_M_~t2~ = `r desc[["t2_inf_sha_beh_m_mean"]] %>% my_round(2)`, 
_M_~t3~ = `r desc[["t3_inf_sha_beh_m_mean"]] %>% my_round(2)`, 
and the standard deviations _SD_~t1~ = `r desc[["t1_inf_sha_beh_m_sd"]] %>% my_round(2)`, 
_SD_~t2~ = `r desc[["t2_inf_sha_beh_m_sd"]] %>% my_round(2)`, and
_SD_~t3~ = `r desc[["t3_inf_sha_beh_m_sd"]] %>% my_round(2)`.
The model fit the data adequately,
`r fit_txt(fit_inf_sha_beh_4)`.
The reliability was high ($\omega$~t1~ = `r reliabilityL2(fit_inf_sha_beh_4, "t1_inf_sha_beh_f")[["omegaL2"]] %>% my_round("std")`, $\omega$~t2~ = `r reliabilityL2(fit_inf_sha_beh_4, "t2_inf_sha_beh_f")[["omegaL2"]] %>% my_round("std")`, $\omega$~t3~ = `r reliabilityL2(fit_inf_sha_beh_4, "t3_inf_sha_beh_f")[["omegaL2"]] %>% my_round("std")`).
Overall, `r icc_inf_sha_beh$ICC_adjusted * 100 %>% round(0)`% of the measure's variance was explained by differences between persons.

@@

Hypothesis 1 predicted that people reporting higher concerns about online privacy than others would also be less likely to share personal information online than others.
Results revealed that the random intercepts of the two variables were significantly correlated (`r coeffs_txt(fit_riclpm, "cor_b_2", one_sided = TRUE)`). 
Hence, respondents who---on average across all three waves---were more concerned about their privacy than others also shared slightly less personal information online.
The effect was small.
However, when looking at the standardized effect's confidence interval (i.e., $\beta$ = `r effect_std_ci[["est.std"]] %>% my_round("std")`, 95% CI [`r effect_std_ci[["ci.lower"]] %>% my_round("std")`, `r  effect_std_ci[["ci.upper"]] %>% my_round("std")`]), it was not significantly smaller than our SESOI of $beta$ = .10.
Thus, Hypothesis 1 was supported.

Hypothesis 2 proposed that if people perceived more concerns about their online privacy than they usually do, they would also share less personal information online than they usually do.
Results revealed a small significant correlation (`r coeffs_txt(fit_riclpm, "cor_w_2", one_sided = TRUE)`), suggesting that if respondents were more concerned about their online privacy at T1 than usual, they also shared less personal information online at T1 than usual.
In conclusion, the results supported Hypothesis 2.

@@

Hypothesis 3.1 predicted that people who perceived more privacy concerns than others would also hold more negative attitudes toward the online sharing of personal information than others. 
The results revealed a medium-sized negative correlation between the two variables on the between-person level (`r coeffs_txt(fit_riclpm, "cor_b_1", one_sided = TRUE)`). 
Thus, people who---on average across all three waves---reported being more concerned about their online privacy relative to the rest of the sample, were also substantially more likely to hold a more negative attitude toward the online sharing of personal information, thereby supporting Hypothesis 3.1.
Hypothesis 3.2 stated that people who held more positive attitudes toward the online sharing of personal information than others would also share more personal information online than others. 
Results showed a very strong between-person correlation between the two variables (`r coeffs_txt(fit_riclpm, "cor_b_3", one_sided = TRUE)`). 
In other words, when averaged across all three waves, if people had more positive attitudes toward the online sharing of personal information than others, they were much more likely to actually share personal information online.
In conclusion, the results supported Hypothesis 3.2.

Hypothesis 4.1 proposed that people who perceived more privacy concerns than usual would also hold more negative attitudes toward the online sharing of personal information than usual. 
The results did not reveal a significant effect (`r coeffs_txt(fit_riclpm, "cor_w_1", one_sided = TRUE)`). 
Hypothesis 4.2 proposed that people who held more positive attitudes toward the online sharing of personal information than usual would also share more personal information online than usual. 
Results showed a moderate within-person correlation between the two variables (`r coeffs_txt(fit_riclpm, "cor_w_3", one_sided = TRUE)`), indicating that when respondents had more positive attitudes toward the online sharing of personal information at T1 than usual, they also shared more personal information online than usual.
In conclusion, the results supported Hypothesis 4.2.

With Research Question 2.1, we analyzed the longitudinal relations of concerns about online privacy and positive attitudes toward the online sharing of personal information. 
No significant effect was found (`r coeffs_txt(fit_riclpm, "b1")`).
Regarding Research Question 2.2, again no significant longitudinal relations emerged between privacy attitudes and privacy concerns 6 months later (`r coeffs_txt(fit_riclpm, "a2")`).

@@

Table \@ref(tab:Results1) presents an overview of all results.

@@

apa_table(
  tab_results
  , caption = "Parameter Estimates Obtained in the Random-Intercept Cross-Lagged Panel Model"
  , note = paste0("The between-person correlations represent interpersonal relations. For example, results showed that people who were more concerned than others, averaged across all three waves, also shared less information than others. The within-person parameters reflect how intrapersonal changes in one variable are related to intra-personal changes in another. For example, results showed that if a person was more concerned at T1 than he or she usually is, he or she also shared less information than usual.")
  , font_size = "small"
  , stub_indents = list("Between-person correlations across all waves" = c(1:3),
                        "Within-person correlations at T1" = c(4:6),
                        "Within-person effects across 6 months" = c(7:12))
  , align = c("l", rep("r", 6))
  , escape = FALSE
  , col_spanners = list(`95\\% CI` = c(3, 4))
#  , placement = "h"
)
```

@@

Current research on the privacy paradox suggests a significant and small relation between concerns about online privacy and the online sharing of personal information [e.g., @baruhOnlinePrivacyConcerns2017]. 
However, whereas the theoretical premise of the privacy paradox actually addresses a within-person effect,
empirical studies have analyzed between-person relations.
On the basis of a representative sample of the German population, from which three waves of data separated by 6 months were collected, we have hence analyzed the privacy paradox by differentiating general between-person relations, short-term within-person relations, as well as long-term within-person effects.

The results of the between-person analyses showed that people who were more concerned about their privacy than others also shared personal information slightly less frequently.
In addition, people who were more concerned about their privacy than others also held substantially more negative attitudes toward disclosing personal information online.
Notably, we found a very strong between-person correlation between attitudes toward information sharing and actual information sharing, implying that typical online disclosure can be precisely predicted by a person's attitude.
Taken together, the cross-sectional results are in line with the extant literature: 
Specifically, the between-person correlation of privacy concerns and information sharing found in this study (i.e., $\beta$ = -.08) fell within the 95% confidence interval of the effect reported by Baruh et al. [-@baruhOnlinePrivacyConcerns2017] (i.e., _r_ = -.13, 95% CI [-.07, -.18]). 
Note that the between-person correlations reported here represent averaged measurements across three waves, thereby rendering the findings comparatively robust. 
In conclusion, this study replicates the finding that the privacy paradox does not seem to exist on a between-person level:
The differences between people with regard to their online information sharing behavior can be explained by differences in privacy concerns to a small extent, and by differences in privacy attitudes to a large extent.

The within-person results showed that when a person's privacy concerns increased, the same person also shared slightly less information online than he or she usually did.
Moreover, we found that people who developed more positive attitudes toward the online sharing of personal information than usual also shared substantially more personal information online.
In conclusion, the results suggest that changes in concerns and attitudes are both partially related to changes in behavior, implying that also on a within-person level the privacy paradox does not seem to exist.
